---
title: "HS.STRC.PA_Dendrograms"
author: "Harry Smith"
date: "6/1/2018"
output: html_document
---


This program takes as input the PA tables created in "HS.STRC.DataRead.Rmd" and uses them to examine clustering at the sample and strain level. For each dataset a dendrogram is generated for the sample level. The dendrograms from the first dataset are used to idenify outlier samples.  These are then removed in "HS.STRC.DataRead.Rmd" and these data are used for the second set of dendrograms (if necessary). 

File input: /Volumes/smiharry/Saba_Lab/RNA-Seq/HS/Transcript_Reconstruction/Brain/quantitation/PA.table.RData
File ouput: /Volumes/smiharry/Saba_Lab/RNA-Seq/HS/Transcript_Reconstruction/Brain/Graphics/

```{r, echo=FALSE, message=FALSE, warning=FALSE}
## Set up workspace
rm(list = ls())
options(stringsAsFactors = FALSE)
library(stcr)
library(WGCNA)
library(RColorBrewer)
## Create global directory objects 
dir <- "/Volumes/smiharry/Saba_Lab/RNA-Seq/HS/"
dirlocal <- "~/Desktop/Saba_Lab/"
tissue <- "Brain"
```

1a. Examine clustering based on present/absent criteria (Using PA.table) - Before removing outliers

```{r, echo=FALSE, warning=FALSE, message=FALSE}

load(file = paste(dir, "Transcript_Reconstruction/", tissue, "/quantitation/",  "PA.table", ".Rdata", sep = ""))

PA.forDendro <- PA.table[, -c(1)]
rownames(PA.forDendro) <- PA.table$transcript_id

# create hierarchical clustering
content.hclust = hclust(as.dist(1-cor(PA.forDendro, method="pearson")))

colors = c(brewer.pal(9, "Set1"), brewer.pal(8, "Set2"))

batch.tmp <-  unlist(lapply(strsplit(content.hclust$labels,split="_",fixed=TRUE),function(a) a[length(a)]))
batch.num <- unlist(lapply(strsplit(batch.tmp,split="batch",fixed=TRUE),function(a) a[length(a)]))

colors4plot2=c()
for(i in 1:length(batch.num)){
  if(batch.num[i]=="1"){colors4plot2[i]=colors[1]}
  if(batch.num[i]=="2"){colors4plot2[i]=colors[2]}
  if(batch.num[i]=="3"){colors4plot2[i]=colors[3]}
  }
colors4plot2=as.matrix(colors4plot2)
colnames(colors4plot2) = "Batch"

labsforbrainregion <- content.hclust$labels

colors4brainregion=c()
for(i in 1:length(labsforbrainregion)){
  if(grepl("AcBc", labsforbrainregion[i], fixed = T)){colors4brainregion[i]=colors[4]}
  if(grepl("IL", labsforbrainregion[i], fixed = T)){colors4brainregion[i]=colors[5]}
  if(grepl("LHB", labsforbrainregion[i], fixed = T)){colors4brainregion[i]=colors[6]}
  if(grepl("PL", labsforbrainregion[i], fixed = T)){colors4brainregion[i]=colors[7]}
  if(grepl("VoLo", labsforbrainregion[i], fixed = T)){colors4brainregion[i]=colors[8]}
  }
colors4brainregion=as.matrix(colors4brainregion)
colnames(colors4brainregion) = "Brain Region"

#plot the dendrogram with a color bar underneath that in this example case corresponds to batch 
pdf("/Volumes/smiharry/Saba_Lab/RNA-Seq/HS/Transcript_Reconstruction/Brain/graphics/TC_SampleLevel_Dendrogram_BeforeFiltering.pdf", height = 10, width = 25)
plotDendroAndColors(dendro=content.hclust, colors=as.matrix(cbind(colors4plot2, colors4brainregion)), main="HS Brain Transcript Content: Present/Absent \n Sample Level", ylab="1-Pearson Correlation",cex.dendroLabels = 0.45)
dev.off()
```
